Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-09 Docs/IJES/journal.tex
resolving comments for IJES

\vspace{2 mm}
It is possible to instruct ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. Those values that change for each test will generate a possible solution and obey the constraints. If this is achieved, then a feasible solution is found and the ASSUME directive is responsible for ensuring the compliance of those constrains (\textit{i.e.}, $A.x \leq b$).

>>>>

\vspace{2 mm}
It is possible to instruct ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. \textcolor{blue}{Those values are selected by the SMT Solver during its execution, which is responsible to test once all possible combinations in order to yield a feasible solution. If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.
